%-------------------------
% Resume in LaTeX
% Author: [Your Name]
% License: MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

% Page setup
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Custom colors
\definecolor{darkblue}{RGB}{26,13,171}
\definecolor{black}{RGB}{0,0,0}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom commands
\newcommand{\resumeSection}[1]{
    \vspace{10pt}
    {\color{darkblue}\hrule}
    \vspace{-5pt}
    \section*{#1}
}

\newcommand{\resumeItem}[2]{
    \item \textbf{#1:} #2
}

\newcommand{\resumeSubItem}[2]{
    \item \textbf{#1} #2
}

\newcommand{\resumeSubHeading}[4]{
    \vspace{-1pt}
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
    \end{tabular*}
}

\newcommand{\resumeSubHeadingSimple}[2]{
    \vspace{-1pt}
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
    \end{tabular*}
}

% Document content begins here
\begin{document}

% Header section
\begin{center}
    \textbf{\Huge Shiva Pal}\\
    \vspace{15pt}
    \href{mailto:shivapalsinghjadaun@gmail.com}{\faEnvelope\ shivapalsinghjadaun@gmail.com} \,|\, 
    \href{https://www.linkedin.com/in/shivapal/}{\faLinkedin\ linkedin.com/in/shivapal} \,|\, 
    \href{https://shivapal98.github.io/shiva/}{\faGlobe\ Github} \,|\,
    \href{+91-7014944922}{\faMobile\ +91-7014944922}
\end{center}

% Summary section
\resumeSection{Summary}
Dedicated and skilled DevOps Engineer and Certified Security Engineer v2 with experience in architecting and managing Linux-based servers, working with multiple cloud providers, and Kubernetes clusters. Proficient in automation scripting and ensuring high uptime and fault tolerance. Skilled in various cloud platforms, technologies, and monitoring tools.

% Experience section
\begin{itemize}[left=0pt]
    \let\olditem\item % Store the current \item command
    \renewcommand{\item}[1][]{\olditem} % Redefine \item to do nothing
    \resumeSubHeading{Growth Natives (Product)}{Mohali, Punjab}{Senior DevOps Engineer}{Apr 2021 - Present}
    \begin{itemize}
        \item Utilized \textbf{IAC} tools like Terraform and Pulumi to create cloud infrastructures.
        \item Created \textbf{CI/CD} pipelines for fully automated code deployment.
        \item Built high-availability infrastructure using AWS EKS, AWS ECS, GCP GKE, Terraform, and HaProxy.
        \item Worked with \textbf{HaProxy} Load Balancer and created service discovery for ECS.
        \item Designed resilient infrastructure on Google Cloud following best practices.
        \item Deployed infrastructures on Digital Ocean using Pulumi, including Kubernetes, MySQL, MongoDB, Helm charts, Ingress controller, and Logging and monitoring stack.
        \item Implemented monitoring and logging stack with Grafana, Loki, Fluentd, and Prometheus.
        \item Automated daily tasks through scripting and addressed vulnerabilities in mailing solutions like Gmail and Outlook.
        \item Secured and rotated credential secrets using \textbf{VAULT}.
    \end{itemize}
\end{itemize}


    % Add more experiences as needed
\end{itemize}

% Key Skills section
\resumeSection{Key Skills}
\begin{itemize}[left=0pt]
    \resumeSubItem{Clouds}{AWS, GCP, Azure, Digital Ocean, Linode, Hetzner, Wpengine}
    \resumeSubItem{GCP}{Cloud Run, GKE, GCS, Compute Engine}
    \resumeSubItem{AWS}{EKS, ECS, ECR, RDS, Auto scaling groups, Cloud Map, S3, IAM, Lambda, CloudWatch}
    \resumeSubItem{Technologies}{Kubernetes, Docker-compose, Gitlab, Ansible}
    \resumeSubItem{IAC}{Terraform, Pulumi, Helm, shell scripts, Python}
    \resumeSubItem{Monitoring}{ELK, Grafana Loki Prometheus stack}
\end{itemize}

% Certifications section
\resumeSection{Certifications}
\begin{itemize}[left=0pt]
    \item {Security Intelligence Engineer, Google Cloud Essential}{}
\end{itemize}


% Education section
\resumeSection{Education}
\resumeSubHeading{Chandigarh University}{Mohali, Punjab}{Bachelor of Engineering in Computer Science}{Aug. 2017 – July. 2021}
\end{document}
